Strong lensing selection effects

### 2022-06-29 paper/seleff.tex
started intro

The third paper of this series \citep[][, hereafter Paper III]{Son22}, showed how to take into account selection effects.

The structure of this work is the following.
I discuss the results in \Sref{sect:discuss} and draw conclusions in \Sref{sect:concl}.

@@

>>>>

\citep{Son22} showed how to correct for selection effects in a population study of a sample of strong lenses. However, the practical realization of the \citep{Son22} method is challenging, as it requires 1) characterising the background source population, 2)

The structure of this work is the following.
In \Sref{sect:indlenses} we study individual lens systems, to look for trends in the lensing cross-section with various lens and source properties.
In \Sref{sect:lenspop} we study

I discuss the results in \Sref{sect:discuss} and draw conclusions in \Sref{sect:concl}.

@@

In this section we study how the probability of a strong lensing event varies as a function of
